\textsc{HubbleCLIP}: Learning associations between astronomical observations and natural language with multi-modal models

### 2023-11-21 paper/main.tex
Text updates

\title{\textsc{HubbleCLIP}: Learning associations between astronomical data and natural language with multi-modal models}

@@

\author{\name Siddharth Mishra-Sharma \email smsharma@mit.edu \\
      \addr The NSF AI Institute for Artificial Intelligence and Fundamental Interactions\\
      Center for Theoretical Physics, Massachusetts Institute of Technology, Cambridge, MA 02139, USA \\
      Department of Physics, Harvard University, Cambridge, MA 02138, USA
      \AND
      \name Yiding Song \email ydsong@mit.edu \\
      \addr The NSF AI Institute for Artificial Intelligence and Fundamental Interactions\\
      Department of Physics, Massachusetts Institute of Technology, Cambridge, MA 02139, USA \\
      \AND
      \name Jesse Thaler \email jthaler@mit.edu \\
      \addr The NSF AI Institute for Artificial Intelligence and Fundamental Interactions\\
      Center for Theoretical Physics, Massachusetts Institute of Technology, Cambridge, MA 02139, USA \\
}
% The \author macro works with any number of authors. Use \AND 
% to separate the names and addresses of multiple authors.

>>>>

\title{\textsc{HubbleCLIP}: Learning associations between astronomical observations and natural language with multi-modal models}

@@

\author{\name Siddharth Mishra-Sharma \email \href{mailto:smsharma@mit.edu}{smsharma@mit.edu} \\
      \addr The NSF AI Institute for Artificial Intelligence and Fundamental Interactions\\
      Center for Theoretical Physics, Massachusetts Institute of Technology, Cambridge, MA 02139, USA \\
      Department of Physics, Harvard University, Cambridge, MA 02138, USA
      \AND
      \name Yiding Song \email \href{mailto:ydsong@mit.edu}{ydsong@mit.edu} \\
      \addr The NSF AI Institute for Artificial Intelligence and Fundamental Interactions\\
      Department of Physics, Massachusetts Institute of Technology, Cambridge, MA 02139, USA \\
      \AND
      \name Jesse Thaler \email \href{mailto:jthaler@mit.edu}{jthaler@mit.edu} \\
      \addr The NSF AI Institute for Artificial Intelligence and Fundamental Interactions\\
      Center for Theoretical Physics, Massachusetts Institute of Technology, Cambridge, MA 02139, USA \\
}
% The \author macro works with any number of authors. Use \AND 
% to separate the names and addresses of multiple authors.
